The letter

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
edits to S1 from David

\ken{I cannot understand the motivation being including this paragraph? I do not feel that this argument has any practical implications; can anyone enlighten me?}
Alternatively, given the basis function width, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis. This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors. To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
\begin{equation}\label{eq:CutoffFromBasisFuncWidth}
	\boldsymbol{\nu}_{c\phi}=\frac{1}{\pi\sigma_{\phi}}\sqrt{\frac{\ln2}{2}}.
\end{equation}

>>>>

\ken{I cannot understand the motivation being including this paragraph? I do not feel that this argument has any practical implications; can anyone enlighten me?}

Alternatively, the basis function width given the basis function width, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis. This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors. To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
\begin{equation}\label{eq:CutoffFromBasisFuncWidth}
	\boldsymbol{\nu}_{c\phi}=\frac{1}{\pi\sigma_{\phi}}\sqrt{\frac{\ln2}{2}}.
\end{equation}

### 2010-06-30 ltx/PLoS/SubmissionLetter.tex
edits to S1 from David

I am writing to seek publication of our research article titled `A Data Driven Framework for Patient-Specific Neural Field Modelling' in PLoS Computational Biology.

This paper brings several new techniques to Computational Biology, where as the title suggests, we have developed a data-driven framework for generating patient-specific neural field models. This paper is timely as it draws together several areas of cutting-edge technologies including:
\begin{itemize}
	\item Recent increases in bandwidths in data acquisition systems, higher resolution recording technology and data storage capabilities have led to significant advances in neurophysiological recording techniques. 
	\item In parallel to these experiment/clinical developments, the development of neural field theory has led to a many insights into the mass action of cortical systems. 
	\item In addition, recent advances in computing power and nonlinear systems theory have made possible state estimation from nonlinear spatio-temporal systems.
\end{itemize}

This work provides an essential link, bridging the data driven and theoretically driven areas of research. We hope that this work will help bring together these previously separated experimental and theoretical communities by providing a framework where both new and existing hypotheses may be tested.

@@

Since this primarily a methods paper, we have taken the option of preceding the results by the methods section.

>>>>

I am writing to seek publication of our research article titled `A Data-Driven Framework for Neural Field Modelling' in PLoS Computational Biology.

This paper brings several new techniques to Computational Biology, where as the title suggests, we have developed a data-driven framework for generating neural field models. This paper is timely as it draws together several areas of cutting-edge technologies including:
\begin{itemize}
	\item increases in bandwidths in data acquisition systems, higher resolution recording technology and data storage capabilities that have led to significant advances in neurophysiological recording techniques, 
	\item developments in neural field theory that have led to valuable insights into the mass action of cortical systems,
	\item recent advances in computing power and nonlinear systems theory that have made possible state estimation from nonlinear spatio-temporal systems.
\end{itemize}

This work provides an essential link, bridging the data-driven and theoretically-driven areas of research. We hope that this work will help bring together these previously separated experimental and theoretical communities by providing a framework where both new and existing hypotheses may be tested.

@@

Due to the novel aspects of the model reduction and estimation procedure, we have taken the option of preceding the results by the methods section.
